%!TEX TS-program = xelatex
%!TEX TS-options = -synctex=1
%!TEX encoding = UTF-8 Unicode
%
%  mog
%
%  Created by Mark Eli Kalderon on 2010-04-06.
%  Copyright (c) 2010. All rights reserved.
%

\documentclass[12pt]{article} 

% Definitions
\newcommand\mykeywords{given, Sellars, perception, reasons} 
\newcommand\myauthor{Mark Eli Kalderon} 
\newcommand\mytitle{Before the Law}

\input{preamble/preamble.tex}

%%% BEGIN DOCUMENT
\begin{document}

% Title Page
\maketitle
% \begin{abstract} % optional
% \noindent
% \end{abstract} 
\vskip 2em \hrule height 0.4pt \vskip 2em
% Main Content
\epigraph{Before the law sits a gatekeeper. To this gatekeeper comes a man from the country who asks to gain entry into the law. But the gatekeeper says that he cannot grant him entry at the moment. The man thinks about it and then asks if he will be allowed to come in sometime later on. “It is possible,” says the gatekeeper, “but not now.”---Franz Kafka}

% Layout Settings
\setlength{\parindent}{1em}

\section{Introduction} % (fold)
\label{sec:introduction}
\noindent It is notoriously difficult to understand the charge of falling prey to the Myth of the Given. The principal obstacle was erected by Sellars himself. The Myth of the Given is said to arise in various forms, and yet each of these forms participates in a framework of givenness---a framework that Sellars declines to specify in general terms. As interpreters of Sellars, we may speculate about how best to understand the general framework of givenness. It is reasonable to attempt to reconstruct that framework in light of Sellars' discussion of the more specific forms of the Myth and especially in light of the conceptual genealogies he offers. However, there is no consensus on how the Myth of the Given is to be understood in general terms even among philosophers sympathetic with Sellars on fundamental issues. Thus different accounts of the Myth are given by \citet{Bonjour:1985sj}, \citet{Brandom:2002fk}, \citet{Coates:2007ly}, \citet{deVries:2005qf}, \citet{McDowell:1996uq,McDowell:1998vn}, \citet{Rosenberg:2007ve}, \citet{Rorty:1979ys}, and \citet{Williams:1977zr}.

Nevertheless, there may be occasions where one can know, or at least reasonably judge, that a conception of perception is a form of the Myth (if it is indeed a myth) without knowing in general terms what the Myth of the Given is. So, for example, I am increasingly attracted to a conception of visual perception as a mode of taking in---as affording the perceiver with a sensory mode of awareness of particulars spatially distant from the perceiver's body. This distinctive sensory mode of awareness is not propositional---it does not take a fact as its object, but a particular. Nor is it in any way the actualization of the subject's conceptual capacities. Moreover, this sensory mode of awareness is fundamental and irreducible. This fundamental and irreducible sensory mode of awareness of spatiotemporal particulars arrayed in a mind-independent environment makes one knowledgeable of that environment. In being so aware of a particular, the perceiver is in a position to know certain things about it, depending, of course, on their possession of recognitional capacities appropriate to the given circumstances. We can be confident that Sellars, at least, would regard this as a form of the Myth since it involves a preconceptual mode of awareness.

Suppose, then, one is liable to the charge of falling prey to the Myth of the Given. How might one respond to the charge? Not directly, it seems. For suppose one could argue that the Myth of the Given was no myth on a specific understanding of that charge. Given the lack of consensus on how the framework of givenness is to be understood, it would remain an open question whether the conception defended was yet another form of the Myth on a distinct and potentially superior understanding of it. A lack of a definitive statement of the Myth from Sellars and a lack of consensus on how best to reconstruct the general framework of givenness renders the charge elusive and Protean. Being liable to the charge is like being the man from the country who seeks access to the law in Kafka's parable. Denied access to law, should one simply despair before its gatekeepers?

While no direct response is possible, perhaps an \emph{indirect} response is. I can think of two complementary strategies. First, one might strive to satisfy oneself that perception, so conceived, is epistemically significant---that the conception renders intelligible that perception should make one knowledgeable of a mind-independent subject matter. Of course, by itself, this would fail to persuade anyone inclined to prosecute that charge, but persuading the prosecution is unnecessary to achieve the modest task of setting one's own mind at ease about the epistemic significance of perception as one conceives it to be. The task may be modest in this way, but it is an essential first step that promises to clarify what is at issue in the dispute. Second, one might examine rival conceptions of perception that are tailor-made to avoid the Myth of the Given such as those provided by \citet{Sellars:1956xp,Sellars:1967uq} and \citet{McDowell:1996uq,McDowell:1998vn,McDowell:2008fk}. If criticism of conceptions designed specifically to avoid the Myth naturally motivates a conception that is known, or reasonably judged, to be a form of the Myth, this is some reason, at least, to think that the Myth of the Given is no myth. 

These, then, are the strategies that I will be pursuing. In the first part, I proceed dogmatically, sketching how visual perception, conceived as a nonpropositional sensory mode of awareness, can make the subject knowledgeable of particulars without the mind (section~\ref{sec:sensory_awareness}). In the second part, I proceed dialectically, discussing Sellars and McDowell on perceptual experience (sections~\ref{sec:sensory_impressions}, \ref{sec:tu_quo_que}, and \ref{sec:selective_presentation_and_synthesis}). Of particular interest will be McDowell's criticism that Sellars misconceives the nature of sensibility by allowing receptivity to operate independently of the subject's conceptual capacities. There are distinguishable claims made in the course of leveling this criticism. Marking these allows us to see that McDowell is right in rejecting Sellars' account, but wrong in thinking that this requires our conceptual capacities to be actualized in perceptual awareness.

% section introduction (end)

\section{Sensory Awareness} % (fold)
\label{sec:sensory_awareness}

Dissatisfaction with the quality of tomatoes available in central London and not a concern for the veracity of philosophical clichés was my reason for growing tomatoes by my window. It is a large plant in a terra cotta pot that sits on a wooden stool set against a generous Victorian window. In the background is a field of rubble where Middlesex Hospital used to be. Everything has been leveled except for the chapel. Looking up I see a ripening tomato set against this complex scene. It is not quite ripe---it is a yellowish red, if not orange. Moreover, it is dappled in sunlight that has just emerged from the clouds in the aftermath of a shower. When I see the ripening tomato, the ripening tomato is the object of my perceptual experience---I am aware of the tomato in my perceptual experience of it. 

The awareness involved in my visual perception is \emph{sensory} in the way that the awareness of a passing thought in the stream of consciousness is not. While perceptual awareness is sensory, sensory awareness need not be perceptual. Pain and proprioception are sensory but are plausibly nonperceptual. Moreover, vision affords the subject with a distinctive \emph{mode} of sensory awareness. Vision is not alone among the senses in providing information about the distal environment. Thus we can \emph{see} the leaves rustling and \emph{hear} them rustling. Perhaps, as \citet[]{Berkeley:1734fk} urged, we hear, at least in the first instance, the sound of the rustling leaves. But, if we do, then, at least in propitious circumstances, we hear the source of the sound by hearing the sound. So whereas vision affords the subject with a \emph{visual} mode of awareness of the event, arguably at least, audition affords the subject with an \emph{auditory} mode of awareness of the very same event. (For recent discussion of audition see \citealt{Nudds:2009sk}).

The objects of visual awareness are spatiotemporal particulars arrayed in a mind-independent environment. These particulars do not constitute a unified ontological category. Among them are objects (the plant, the stool), events (the rustling of the leaves, the sun's setting), and property instances (the yellowish red of the tomato). But objects, events, and property instances have distinct modes of being. Thus, for example, events are spatiotemporal particulars that unfold through time in a way that neither objects nor property instances do (though see \citealt{Sider:1997fk} for criticism of this way of distinguishing events from objects; see also \citealt{Hawthorne:2008uq} and \citealt{Fine:2006fk} for further discussion). The particulars that we see also differ in degree of both substantiality and being. In addition to ordinary material substances like tomatoes, we see flashes, flames, reflections, and rainbows, on the one hand, and shadows and holes, on the other hand. Flashes are unusual events. They are colored, but most events are not colored despited having colored participants. (What color was the Battle of Kosovo?) But what is presently important is that they also lack substrata. And the plant's shadow is constituted by a relative decrease in the amount of light uniformly distributed across the visible spectrum in a region determined by the positions of the plant, the light source, and the surface on which the shadow is cast. But a relative decrease is a privation or diminution of being \citep[see][]{Sorensen:2008kx}. Shadows may be creatures of darkness, but perception makes shadows, a species of privation, the subject matter of demonstrative thought and talk. Despite being particulars, the objects of perception differ, in this way, in mode, substantiality, and being. (On the heterogeneity of the objects of visual perception see \citealt{Austin:1962lr}.)

Vision makes spatially distant particulars visually present. When I see the yellowish red tomato, I see a particular spatially distant from me. Moreover, I experience the yellowish red as inhering in the external surface of that particular. Hering's \citeyearpar[8]{Hering:1920ty} ringed shadow experiment demonstrates the phenomenological difference between a color merely overlaying a surface and that color inhering in that surface. When a shadow is cast on a white surface you see the shadow as ``an incidental darkness that lies on the [surface]''. If now a black line is drawn around the shadow completely obscuring its penumbra, the darkness no longer appears to lie on the surface, but rather appears to inhere in the surface. Only then does the shadowed white surface misleadingly look to be gray. Of course, not all colors inhere in substances or their parts. A flash can be blue even though the flash lacks a substrata in which the blue could inhere. But even if the blue of the flash inheres in nothing, I experience the blue in the remote spatiotemporal region of the flash. 

Thus, Broad writes:
\begin{quote}
    In its purely phenomenological aspect \emph{seeing} is ostensibly \emph{saltatory}. It seems to leap the spatial gap between the percipient's body and a remote region of space. Then again, it is ostensibly \emph{prehensive} of the surfaces of distant bodies as coloured and extended, and of external events as colour-occurences \emph{localized} in remote regions of space. \citep[32]{Broad:1965dq}
\end{quote}
Seeing is saltatory in that the objects of visual awareness are spatially remote; seeing is prehensive in that its objects are present in our visual awareness of them. ``Prehensive'' belongs to a primordial family of broadly tactile metaphors for visual awareness that includes ``grasping'', and ``apprehending''. What unites these metaphors is that they are all a mode of taking in, and ``ingestion'' is a natural variant \citep[see][7]{Johnston:2006uq,Price:1932fk}. The tactile nature of these metaphors can mislead, however, if we take too seriously the contact involved in taking in an object. Thus \citet[33]{Broad:1965dq} remarks that ``It is a natural, if paradoxical, way of speaking to say that seeing seems to `bring us into \emph{contact} with \emph{remote} objects' and to reveal their shapes and colors''. The air of paradox, however, is removed once we recognize that the sense in which visual awareness brings us into contact with particulars does not conflict with the sense in which these particulars are remote. To be sure, seeing the tomato a meter away does not make the tomato proximate, but that just means that the sense in which the tomato is present in visual awareness is not the same sense as the tomato being spatially present.

The phenomenology of being visually presented with colors inhering in external bodies played a role in Russell's felt exuberance in abandoning idealism:
\begin{quote}
	I felt it, in fact, as a great liberation, as if I had escaped from a hothouse on to a wind-swept headland. I hated the stuffiness involved in supposing that space and time were only in my mind. I liked the starry heavens even better than the moral law, and could not bear Kant’s view that the one I liked best was only a subjective figment. In the first exuberance of liberation, I became a naïve realist and rejoiced in the thought that grass is really green, in spite of the adverse opinions of all philosophers from Locke onwards. \citep[48]{Russell:1959fv}
\end{quote}
What Russell rejoiced in was warrantedly taking external bodies to be the way his perceptual experience presents them to be---as having colors inhering in the opaque surfaces they present. He rejoiced in the greenness of the grass revealed by sight. Compare Melville's earlier revulsion at Locke's \citeyearpar{Locke:1706hc} metaphysics:
\begin{quote}
	And when we consider that other theory of the natural philosophers, that all other earthly hues---every stately or lovely emblazoning---the sweet tinges of sunset skies and woods; yea, and the gilded velvets of butterflies, and the butterfly cheeks of young girls; all these are but subtile deceits, not actually inherent in substances, but only laid on from without; so that all deified Nature absolutely paints like the harlot, whose allurements cover nothing but the charnel-house within \ldots\ \citep[ch. 42]{Melville:1851ms}
\end{quote}
Freed from the adverse opinions of all philosophers from Locke onwards, one need no longer think that Nature paints like a harlot and can once again rejoice in the lovely emblazoning of an English pastoral scene. The phenomenology of being presented with colors inhering in external bodies is what renders this response intelligible.

Visual perception involves a sensory mode of awareness that takes external particulars as objects. This is a claim about sense perception, not sense experience (understood as the genus of which sense perception is a species). It echoes a conception of perception common among early twentieth century realists. There are, of course, important differences between the present conception and its early twentieth century precursors, just as there were important differences between the Cambridge and Oxford realists. Thus, contra the present conception, \citet[]{Russell:1912uq} held that we are acquainted with universals as well as particulars. And \citet[]{Russell:1912uq} and \citet[]{Price:1932fk} held that the distinctive sensory mode of awareness was operative not just in sense perception but in sense experience more generally. They were thus committed to a kind of \emph{experiential monism} (in Snowdon's \citeyear{Snowdon:2008oz} terminology). Specifically, all sense experience was conceived to involve, as part of its nature, a sensory mode of awareness. According to the Cambridge realists, then, even subject to illusion or hallucination, there is something of which one is aware. But with that, they were an application of the argument from illusion, or hallucination, or conflicting appearances away from immaterial sense data and a representative realism that tended, over time, to devolve into a form of phenomenalism. In contrast, the Oxford realists, \citet{Cook-Wilson:1926sf} and \citet[]{Prichard:1906gf,Prichard:1909yg}, restricted sensory awareness to perception, thus avoiding experiential monism and its degenerative effects \citep[see][]{Marion:2000kl,Marion:2000ai,Kalderon:2010fk}. For present purposes, it suffices to accept only what is common to Cambridge and Oxford realism---that perception involves a sensory mode of awareness whose objects exist independently of that awareness. 

Sellars observes that if sensory awareness takes particulars as objects, then it cannot be a form of propositional knowledge:
\begin{quote}
	[W]e may well experience a feeling of surprise on noting that according to sense-datum theorists, it is \emph{particulars} that are sensed. For what is \emph{known}, even in non-inferential knowledge, is \emph{facts} rather than particulars, items of the form \emph{something's being thus and so} or \emph{something's standing in a certain relation to something else}. It would seem, then, that the sensing of sense contents \emph{cannot} constitute knowledge, inferential \emph{or} non-inferential \ldots\ \citep[§3]{Sellars:1956xp}
\end{quote}
What's known are thoughts, propositions, facts\----\-not par\-ti\-cu\-lars. Sellars does not give us a reason for distinguishing thoughts and particulars in this way. Perhaps he regards the distinction as evident. Prichard, however, gives us a reason, indeed, the right kind of reason. According to Prichard, thoughts have a kind of generality that precludes them from being particulars:
\begin{quote}
	There seems to be no way of distinguishing perception and conception as the apprehension of different realities except as the apprehension of the individual and the universal respectively. Distinguished in this way, the faculty of perception is that in virtue of which we apprehend the individual, and the faculty of conception is that power of reflection in virtue of which a universal is made the explicit object of thought. \citep[]{Prichard:1909yg}
\end{quote}
Prichard's claim about the faculty of conception is what provides a reason for distinguishing thoughts and particulars, and Sellars could accept that reason even if he would reject Prichard's claim about the faculty of perception. (For contemporary discussion of particularity and the content of perception see \citealt{Brewer:2008fk}, \citealt{Martin:2002jb}, \citealt{Soteriou:2000iz,Soteriou:2005fk}, and \citealt{Travis:2005ys}.)

But suppose we accept Prichard's claim that ``the faculty of perception is that in virtue of which we apprehend the individual''. If visual awareness takes particulars as objects, it is not a form of propositional knowledge. But that does not mean that vision, so conceived, lacks epistemic significance. Vision can be a source of knowledge insofar as the perceiver can recognize the object of perception for what it is. When I look at the ripening tomato, the tomato is present in my awareness of it. Moreover, if I possess the appropriate recognitional capacities, in being so aware of the ripening tomato, I can come to know various things about it---that it is yellowish red, say. The nonpropositional sensory mode of awareness involved in visual perception may not be a form of knowledge, but it makes me \emph{knowledgeable} of its object. Sensory awareness makes the subject knowledgeable of its object in the sense that it makes knowledge about its object \emph{available} to the perceiving subject. Vision would make the subject knowledgeable of its object even if, in the circumstances of perception, the subject lacked the conceptual capacities for knowing some range of propositions. Suppose the subject subsequently acquired the relevant conceptual capacities, in recalling the object of sight, the subject might recognize what they had seen and thus acquire propositional knowledge. So even if in the circumstances of perception the subject lacks the relevant conceptual capacities for knowing some proposition, vision can make knowledge of that proposition available. Perception constitutes a change in the subject's knowledge potential whether or not such knowledge is in fact activated (in Williamson's \citeyear{Williamson:1990uq} terminology).

In looking at the ripening tomato by my window, I see the yellowish red of the tomato. If I recognize what I thus see, I can come to know that the tomato is yellowish red. What I know is a proposition---that the tomato is yellowish red. What I see is a particular---the yellowish red of the tomato. How can awareness of that particular make available knowledge of that proposition? Knowledge is a factive attitude born only to true propositions. The objects of perceptual awareness are epistemically significant because of an alethic connection between them and potentially known propositions. The yellowish red of the tomato is a \emph{truthmaker} of the proposition that the tomato is yellowish red \citep[see][]{Johnston:2006uq}. It is impossible for the yellowish red of the tomato to exist and the proposition that the tomato is yellowish red to be false. More generally, I accept a version of \emph{truthmaker necessitarianism}:
\begin{quote}
	If a particular, \( x \)---be it an object, event, or property instance---is a truthmaker for a proposition, \( p \), then it is necessary that if \( x \) exists, then \( p \) is true. 
\end{quote}
\citep[for a survey of recent work on truthmakers see][]{Rodriguez-Pereyra:2006fk}. What is the nature of the modality involved in this claim? I am tempted to say that it is logical necessity, though, of course, a sense of logical necessity distinct from model-theoretic definitions associated with formal systems  \citep[for doubts about model-the\-o\-re\-tic definitions of logical necessity see][]{Etchemendy:1988et,Etchemendy:1988sa}. Nevertheless, the relevant modality deserves to be described as logical necessity, at least in a broader sense, since the source of the necessity flows from the nature of truth. Visual awareness is epistemically significant insofar as its object is the truthmaker of potentially known propositions. Vision makes me knowledgeable of particulars arrayed in a mind-independent environment by making me aware of sensible truthmakers.

Sellars famously connects knowledge and reasons in the following fashion:
\begin{quote}
	The essential point is that in characterizing an episode or state as that of \emph{knowing}, we are not giving an empirical description of that episode or state; we are placing it in the logical space of reasons, of justifying and being able to justify what one says. \citep[§36]{Sellars:1956xp}
\end{quote}
Sellars undertakes a number of separable commitments in this passage, but suppose at least this much---that we can only know what we have reason to judge. It is natural to think that vision is a potential source of knowledge only insofar as it makes the subject aware of what reasons there are. But now suppose further that reasons must have a propositional structure---either by being, or being individuated by, true propositions, or by being states or events with true propositional contents \citep[see][141, 143--4]{McDowell:1996uq}. Insofar as visual awareness takes particulars as its objects it lacks a propositional structure. But this would preclude it from the space of reasons. Seeing the tomato, at least as presently conceived, could not be an awareness of what reasons there are and so could not be a potential source of knowledge.

Not all philosophers accept that knowledge requires the possession of reasons \citep[see][for a recent expression of skepticism]{Pryor:2007fk}. But even granting that knowledge involves reasons, the argument can be resisted insofar as it involves a substantive and controversial claim about the metaphysics of reasons---that reasons must have a propositional structure. Against this, let me dogmatically assert my adherence to a radically externalist conception of reasons \citep[see][]{Dancy:2002fk,Scanlon:1998hb,Raz:2000tm}. The conception is \emph{externalist} in that, according to it, reasons need not be propositional attitudes or any other psychological state of a subject. External reasons may not be propositional attitudes, but, for all that has been said, they may yet have a propositional structure. Suppose reasons are facts. Facts are not psychological states of a subject---not even facts about the psychological states of a subject count. Nevertheless, facts have the structure of the true propositions that represent them (trivially, if facts are true propositions). What makes the present conception \emph{radically} externalist is that, according to it, nonpsychological reasons need not have a propositional structure.

On this conception, the yellowish red of the tomato is a reason for thinking that the tomato is not quite ripe. Note well, it is the yellowish red of the tomato, and not my seeing that the tomato is yellowish red, nor my believing that the tomato is yellowish red, which is a reason. The yellowish red of the tomato lacks a propositional structure---it is a particular, a property instance. It is spatially distant from me---the yellowish red inheres in the opaque surface of the tomato a meter away and inherits its location from the surface in which it inheres. It is an aspect of how things are independently of me. The yellowish red of the tomato is a reason that warrants judging that the tomato is yellowish red. Indeed, in this instance, there could be no better reason---the yellowish red of the tomato warrants judging that the tomato is red because the former makes true the latter. Of course, not all reasons are of this form. The yellowish red of the tomato is also a reason, in certain circumstances, for thinking that the tomato is unripe, but the yellowish red of the tomato does not make it true that the tomato is unripe; at best, it is sign or symptom of the fruit's relative maturity. From this perspective, Davidson's \citeyearpar[310]{Davidson:1986uq} claim that ``nothing can count as a reason for holding a belief except another belief'' seems like an unwarranted form of psychologism (in something like Travis' \citeyear{Travis:2006fk} sense). Of course, in order for the yellowish red of the tomato to rationally bear on what I am to think, it must be cognitively accessible. But that is what perception does for me---perception makes me aware of what reasons there are. Perception is thus a mode of reasonableness (in Scanlon's \citeyear[]{Scanlon:1998hb} sense; for further relevant discussion see \citealt{Ayers:2004kx} and \citealt{McDowell:2009ys}).

In seeing a particular, the subject is in a position to know certain things about it. Being thus knowledgeable endows the subject with a kind of authority. This authority is a \emph{power}---the subject can possess this authority without exercising it. If in seeing the yellowish red of the tomato I am knowledgeable of that particular, then I am warranted in judging that the tomato is yellowish red whether or not I so judge. But if I do, then, at least in propitious circumstances, I thereby come to know that the tomato is yellowish red. The warrant, here, should be understood as an entitlement to judge (in the ordinary sense of ``entitlement'' and not in Burge's \citeyear{Burge:2003fk} technical sense of the term; compare \citealt[132n]{McDowell:2009ys}). It is not a factor in terms of which knowledge could be analyzed or otherwise explained. Moreover, it is an \emph{epistemic} entitlement: The object of my awareness, the yellowish red of the tomato, is a reason that warrants, in the given circumstance, my judging that the tomato is yellowish red where so judging is \emph{coming to know}. Vision confers this epistemic entitlement given the alethic connection between the particular that is the object of visual awareness and the proposition potentially known. Awareness of the sensible truthmaker of a proposition affords the subject with a reason that is in this way akin to proof---it is logically impossible for the particular to exist and the proposition to be false \citep[see][]{Cook-Wilson:1926sf,Kalderon:2010fk,Travis:2005kx}. Because in seeing the yellowish red of the tomato I possess a reason that would, in the given circumstance, warrant my coming to know that the tomato is yellowish red, I am authoritative about the yellowish red of the tomato. My seeing the yellowish red of the tomato can stand proxy for any inquiry on your part about the color of the tomato. If in coming to know that the tomato is yellowish red, I express my knowledge by stating it, I extend to you an offer to take it on my authority that the tomato is the color that I see it to be. 

% section sensory_awareness (end)

\section{Sensory Impressions} % (fold)
\label{sec:sensory_impressions}

Perception involves the subject's sensitivity to a mind-independent environment. In seeing the tomato, I am sensitive to its presence in my immediate environment. Moreover, this seems to be a constitutive feature of perception. If the regular occurrence of a conscious state kind were insensitive the mind-independent environment, it would not be a perceptual state. But it is a further commitment to claim that this sensitivity can be understood independently of the sensory awareness of the perceived object. Perception may be a mode of sensitivity, but it does not follow that the perceiver's sensitivity to the environment is a reductively identifiable independent factor in perception, one that can be individuated independently of the perceiver's sensory awareness. Nevertheless, Sellars' conception of sensory impressions commits him to just such a reductive understanding of perceptual sensitivity.

There are two aspects of sensory impressions as Sellars conceives of them. First, impressions are conscious states of a subject with a phenomenological character. While impressions are conscious states, there is nothing that they are a consciousness \emph{of}. Impressions are nonintentional. Thus Sellars thinks that it is a conflation:
\begin{quote}
    \ldots\ to assimilate ``having a sensation of a red triangle'' to ``thinking of a celestial city'' and to attribute to the former \ldots\ the `intentionality' of the latter. \citep[§7]{Sellars:1956xp}
\end{quote}
Sellars thus conceives of impressions on the model of Kantian sensations. According to \citet[B376--7]{Kant:1781fk}, a sensation ``relates to the subject as a modification of its state'' and contrasts with  an intuition in that only the latter is ``immediately related to the object''. Second, impressions are the effects of the distal environment on the conscious subject. Seeing that something is some way involves a reliable differential responsiveness to objects, events, and properties of the mind-independent environment or facts about these. This reliable differential responsiveness determines no strict correlation. The relationship between distal causes and modifications of the conscious subject is many--one---the same impression involved in seeing that something is the case would be involved in something merely looking to be the case. Thus \citet[§7]{Sellars:1956xp} writes that ``The core idea is that the proximate cause of such a sensation is \emph{only for the most part} brought about by the presence in the neighborhood of the perceiver of a red and triangular physical object''. This reliable differential responsiveness is a species of sensitivity, more generally. In \emph{Science and Metaphysics}, \citet[4]{Sellars:1967uq} describes it as ``sheer receptivity''.

Sellars considers two arguments for the claim that perceptual awareness involves impressions. Each corresponds to the two aspects of his conception of them. In ``Empiricism and the Philosophy of Mind'', Sellars argues that the postulation of impressions arises ``in the attempt to explain the facts of sense perception in a scientific style'':
\begin{quote}
    How does it happen that people can have the experience they describe by saying ``It is as though I were seeing a red and triangular physical object'' when either there is no physical object there at all, or, if there is, it is neither red nor triangular? The explanation, roughly, posits that in every case in which a person has an experience of this kind, whether veridical or not, he has what is called a `sensation' or `impression' `of a red triangle'.  \citep[§7]{Sellars:1956xp}
\end{quote}
\cite[§7]{Sellars:1956xp} does not directly endorse the explanation ``in a scientific style'', immediately commenting that he will ``have a great deal more to say about this kind of `explanation' of perceptual situations in the course of my argument''. Indeed, this may be, at least in part, a dialectical concession to the sense-datum theory corresponding, as it does, to the generalizing step of the argument from illusion. As I read ``Empiricism and the Philosophy of Mind'', Sellars' \citeyearpar[§7]{Sellars:1956xp} argument against the sense-datum theory does not rest with the the charge that ``the classical concept of a sense datum'' is ``a mongrel resulting from the crossbreeding of two ideas''---a nonclassical concept of a sense datum may yet be free of the mongrel conflation \citep[for substantive reasons why Sellars' case against the sense-datum theory could not rest with the mongrel conflation see][]{Snowdon:2009uq}. In §10, Sellars claims that ``a reasonable next step would be to examine these two ideas and determine how that which survives criticism in each is properly to be combined with the other.'' This task will occupy him for the rest of the work, and the sense-datum theory is not completely dispensed with until the penultimate paragraph. Nevertheless, in some passages, Sellars endorses key elements of the explanation. Thus Sellars is plausibly read as claiming that impressions are ``the common descriptive content'' of seeings and lookings \citep[see][167]{Williams:2008fk}. % Since it is unclear whether and to what extent Sellars endorses the explanation ``in a scientific style'', I will set it aside.

While the explanation ``in a scientific style'' focuses on the phenomenological aspect of sensory impressions, the argument in \emph{Science and Metaphysics} focuses on their environmental sensitivity:
\begin{quote}
    \ldots\ it is only if Kant distinguishes the radically nonconceptual character of sense from the conceptual character of the synthesis of apprehension in intuition \ldots\ and, accordingly \emph{receptivity} of sense from the \emph{guidedness} of intuition that he can avoid the dialectic which leads from Hegel's \emph{Phenomenology} to nineteenth century idealism. \citep[16]{Sellars:1967uq}
\end{quote}
McDowell reconstructs Sellars' reasoning as follows:
\begin{quote}
    Sellars thinks that conceptual representations in perception must be guided by manifolds of ``sheer receptivity'', because he thinks that only so can we make it intelligible to ourselves that conceptual occurrences in perceptual experience---and thereby ultimately thought, conceptual activity, in general---are constrained by something external to conceptual activity. And as he sees, we need such external constraint in our picture if we are to be entitled to take it that conceptual activity is directed towards an independent reality, as it must be if it is to be intelligible as conceptual activity at all. \citep[46]{McDowell:1998vn}
\end{quote}

That impression are states of a conscious subject that reliably differentially respond to a mind-independent environment captures the idea that perceptual sensitivity is the \emph{perceiver's} sensitivity to that environment. Perceptual sensitivity is a capacity properly attributable to the perceiving subject. However, impressions are \emph{nonintentional} states of a conscious subject. They take neither environmental particulars nor states of the environment as their object, for they have no object. Since impressions are nonintentional states of a conscious subject with a distinctive phenomenological character, they are individuated independently of the perceiver's sensory awareness of the environment. And since the reliable differential response and its environmental trigger can each be individuated independently of the perceiver's awareness of the environment, and their interaction is a transaction in Nature, Sellars, in conceiving of perceptual sensitivity in terms of manifolds of ``sheer receptivity'', conceives of sensitivity as a reductively identifiable independent factor in perception. Indeed, the manifolds of ``sheer receptivity'' must enjoy this kind of independence if they are to play their guiding role in the synthesis of apprehension in intuition.

Thus while Sellars may not be a conjunctivist, he shares an important commitment with the conjunctivist, in that the reliable differential responsiveness to the mind-independent environment must be individuated independently of the subject's awareness of that environment. Conjunctivism is here understood as a claim about sense perception, if not sense experience more generally. According to the conjunctivist, the reliable differential responsiveness to the environment is a necessary if not sufficient condition for perceptual awareness that can be conjoined with other necessary conditions that are not only jointly sufficient but also constitute an \emph{analysis} of perceptual awareness. Then, on pain of circularity, the reliable differential responsiveness must be specified independently of the subject's perceptual awareness. Contrast this with a nonreductive conception of perceptual sensitivity. If perceptual sensitivity is, or is constituted by, perceptual awareness, then perceptual awareness could not be analyzed in terms of perceptual sensitivity. On this conception, perceptual awareness is a mode of sensitivity, but perceptual awareness is not analyzable or otherwise explained in terms of sensitivity reductively understood. Sellars may not be advancing a conjunctive analysis of perception, but he is committed to perceptual sensitivity being a reductively identifiable independent factor in perception given the explanatory role manifolds of ``sheer receptivity'' play in intuition.

Against this, McDowell maintains that while perceptual experience must be guided from without if a realism, or at least an anti-idealism, is to be sustained, there is no need for manifolds of ``sheer receptivity'' to play this guiding role:
\begin{quote}
    \ldots\ once we understand how objects can be immediately present to conceptually shaped sensory consciousness in intuition, we can take this need for external constraint to be met by perceived objects themselves. \citep[46]{McDowell:1998vn}
\end{quote}
McDowell is making negative and positive claims here. The negative claim is a kind of anticonjunctivism---perceptual sensitivity is, or is constituted by, objects in the mind-independent environment being present in sensory awareness in a way that precludes perceptual sensitivity being a reductively identifiable independent factor in perception and, hence, guidance by manifolds of ``sheer receptivity''. The positive claim is that objects in the mind-independent environment are present in sensory awareness in virtue of the sensory actualization of the subject's conceptual capacities. Importantly, these negative and positive claims are logically independent.

Why is it a mistake to conceive of perceptual sensitivity independently of perceptual awareness? Why is anticonjunctivism mandatory?

Consider a counterfactual reduction of perceptual sensitivity. One might try to give such a reduction on the model of Nozick's \citeyearpar{Nozick:1981fk} tracking theory. Roughly speaking, perceptual sensitivity would be the counterfactual covariation of sense experience and the truth of a potentially known proposition \( p \) through a sphere of possibilities that extends to the nearest not-\( p \) world. On the Stalnaker-Lewis semantics for counterfactuals, the sphere of possibilities is determined by a conversationally salient similarity metric. The reductive ambitions of the account constrains admissible metrics, however. The relevant similarity metric could not be \emph{perceptual}, if perceptual sensitivity is to be specified independently of perceptual awareness. But it is precisely this feature that gives rise to a pattern of counterexamples. It is true that in paradigmatic cases, seeing something can survive small changes in the object, the circumstances of perception, or the perceiver, even where these changes occur along reductively admissible dimensions. But this counterfactual covariation is not true of perception generally.  As \citet{Johnston:2006uq} observes, small changes can sometimes result in a failure to perceive. Consider another experimental subject of Frankfurt's \citeyearpar{Frankfurt:1969kx} Dr Black. A device is surgically implanted that will cut off the flow of information from the optic nerve if a predefined target is not confined to some region of the visual field. Should the target exit that region---by the target moving with respect to the perceiver, or the perceiver moving with respect to the target, without corresponding adjustments---then the optic nerve will be temporarily disabled, for thirty seconds, say. After the device is implanted, the subject recovers from surgery with the target within the region. Small changes in the object or the perceiver---the target moving slightly, or the perceiver's gaze moving slightly---would result in temporary blindness. But that is consistent with the subject seeing the target upon regaining consciousness. Conversely, small changes can sometimes result in the subject seeing something that they previously could not. Consider an object hidden from view by a fragile camouflage that can only be sustained in narrowly defined viewing conditions. Small changes to these viewing conditions would reveal what the camouflage had previously hidden from view. The subject would see the object that they previously failed to see.

Schaffer summarizes the general problem well:
\begin{quote}
    Human perceptual competence forms a discontinuous scatter in logical space. \ldots\ The tracking theory identifies knowledge with counterfactual covariation of belief and truth through a sphere of possibilities. The contents of the sphere are determined by the similarity metric. Derailings occur because the similarity metric (on any reasonable interpretation) is completely out of alignment with our actual rough-and-ready perceptual capacities. The problem is systematic: the mismatch between the smoothness of logical space and the roughness of human perception is not likely to be fixed by a further epicycle. \citep[42]{Schaffer:2003vn}
\end{quote}
The present tracking theory identifies perceptual sensitivity with counterfactual covariation of sense experience and the truth of potentially known propositions through a sphere of possibilities. But the discontinuous scatter that human perceptual competence forms on the relevant sphere of possibilities presents the very same problem. Moreover, the discontinuous scatter is exactly what you would expect, if perceptual sensitivity were identical to, or constituted by, perceptual awareness. 

Not only is the tracking theory subject to a pattern of counterexample, but the best case for the tracking theory undermines its reductive ambitions as well. In paradigm cases where seeing something can survive small changes, sense experience counterfactually covaries with the truth of a potentially known proposition \emph{because} sense experience affords the perceiver awareness of its environmental subject matter. Suppose my seeing the yellowish red of the tomato is such a paradigm case. My seeing the yellowish red of the tomato would survive small changes in the object, the circumstances of perception, or the perceiver. Thus I would still see the yellowish red of the tomato even if the tomato were slightly smaller, or the illumination were brighter, or I viewed it from a different vantage point. My sense experience counterfactually covaries with the truth of the proposition that the tomato is yellowish red because my sense experience affords me awareness of the yellowish red of the tomato, a particular that makes true that proposition. In the first instance, it is the presence of particulars and not the truth of propositions, that we track in vision. Since perceptual awareness of environmental particulars grounds the counterfactual covariation in paradigm cases, the counterfactual covariation could not be the basis of a reductive understanding of perceptual sensitivity.

While McDowell would be unsurprised by reductive failure, I believe that his anticonjunctivism has deeper roots. I suspect that he is moved by a Hegelian thought that an illicit dualism of mind and world could only be overcome if perceptual sensitivity is, or is constituted by, perceptual awareness. If perceptual sensitivity is understood reductively, it would not unite the subject with the distal object the way perceptual awareness would---in Broad's \citeyearpar{Broad:1965dq} terminology, it would not be a mode of prehension. It is hard to make this idea precise, but we can begin to get a handle on it by the way it is manifest in McDowell's metaphor of perceived objects ``shaping'' sensory consciousness. Importantly, the metaphor of ``shaping'' should be read in a constitutive rather than a merely causal sense. Fish explains the contrast as follows:
\begin{quote}
	Consider the following scenario: looking down at a glacial valley, I say to you, ``Can you see how the glacier shaped the contours of the landscape?'' Here `shaping' is being used in the causal sense---the glacier shaped the contours of the landscape by causing elements of the landscape to be the shape they are. \ldots\ But if I were to ask instead ``Can you see how the sides of the hill shape the contours of the landscape?'' I would be using `shaping' not in a causal sense but rather in a constitutive sense---on this reading, the hillsides shape the contours of the landscape by actually \emph{being} the contours of the landscape. \citep[6]{Fish:2009fk}
\end{quote}
Read constitutively, then, objects shape the contours of sensory consciousness by \emph{being} the contours of sensory consciousness. Perception would be constitutively linked to the objects in the environment present in sensory awareness. In contrast, sensory impressions are shaped by the environment in a merely causal sense. Indeed this is central to the Platonic metaphor. Just as a stylus impinging on a wax tablet causes an impression, the environment impinging on a subject with the appropriate sensory capacities causes a sensory impression. But perceptual sensitivity is more than just the environment impinging on the state of a conscious subject. The environment shapes sensory consciousness in a constitutive rather than merely causal sense. Perception is guided from without by being constitutively linked to objects in the environment present in sensory awareness. So conceived, perceptual awareness is a mode of sensitivity, but perceptual awareness is not analyzable or otherwise explained in terms of sensitivity reductively understood. Guidance by manifolds of ``sheer receptivity'' is thus precluded.

% section sensory_impressions (end)

\section{\emph{Tu Quo Que}} % (fold)
\label{sec:tu_quo_que}

McDowell's negative claim---that perceptual sensitivity is not a reductively identifiable independent factor in perception---is logically independent of his positive claim---that perception is the sensory actualization of the subject's conceptual capacities. There is nothing in anticonjunctivism that requires our conceptual capacities to be actualized in perceptual awareness. Consider the conception of perception as a mode of taking in dogmatically sketched in section~\ref{sec:sensory_awareness}. Not only is the conception of perception as a nonpropositional sensory mode of awareness \emph{consistent} with anticonjunctivism, but that conception \emph{requires} anticonjunctivism as well. Perception, so conceived, is constitutively linked to the objects of sensory awareness. As such, the guidance is supplied by the objects being present in sensory awareness. Indeed, it provides a reasonable interpretation of the unity of mind and world that perception affords: Perception is a state of the conscious subject that has, as part of its nature, an external particular as a constituent. Perception is a mode of taking in. So conceived, perception is a mode of sensitivity to spatiotemporal particulars arrayed in the mind-independent environment, but the sensory awareness involved in perception is not analyzable or otherwise explained in terms of sensitivity reductively understood. That is the advertised sense in which the nonpropositional sensory mode of awareness is fundamental and irreducible. 

McDowell's criticism of Sellars is thus susceptible to the following \emph{tu quo que}: 
\begin{quote}
    Perceptual experiences must be guided from without. And indeed they are, I can say. But there is no need for conceptual representations to play this guiding role. In a way that we are now equipped to understand, given the conception of perception as a mode of taking in, that is, as a nonpropositional sensory mode of awareness of external particulars, the guidance is supplied by the objects being present in sensory awareness. Once we understand how objects can be present in sensory awareness, we can take this need for external constraint to be met by perceived objects themselves, irrespective of any conceptual goings-on.
\end{quote}

If perception is a mode of taking in, the objects of perception constitutively shape sensory consciousness (compare Martin's \citeyear[64]{Martin:2004fj}, application of the meta\-phor in characterizing naïve realism). An external particular shapes perceptual experience by being a constituent of that experience. In seeing the tomato ripening by my window, the tomato is present in my awareness of it. My perception of the tomato is not merely causally or counterfactually linked to the presence of the tomato, my perception is constitutively linked to the perceived tomato. And since my perception is constitutively linked to the tomato, the tomato, itself dappled in sunlight and shadow and partially obscuring the view of the chapel, shapes the contours of my sensory consciousness by being present in that consciousness.

In contrast, McDowell's application of the metaphor is equivocal. Sometimes conceptual representations shape sensory consciousness. Sometimes it is their environmental subject matter. While the latter is nearer the mark, it is hard to understand how the subject matter of conceptual representations, rather than the conceptual representations themselves, can be said to shape sensory consciousness if perception is a sensory actualization of conceptual capacities. It is at the very least unobvious why sensory presentation is a species of conceptual representation. Why must perceptual awareness involve the actualization of conceptual capacities?

% section tu_quo_que (end)

\section{Synthesis, Selective Presentation, and The Ineffable} % (fold)
\label{sec:selective_presentation_and_synthesis}

That objects in the mind-independent environment are present in sensory consciousness is what drives McDowell's anticonjunctivism. But it is the conceptual character of perception that prevents this from lapsing into the Myth of the Given. Reflection on Kant's thesis:
\begin{quote}
    The unity to the various representations in a judgment also gives unity to a mere synthesis of various representations in an intuition. \citep[A79/B104--5]{Kant:1781fk}
\end{quote}
is meant to show how this could be so.

Suppose we take \citet[B130]{Kant:1781fk} at his word when he claims that ``all combination, be we conscious of it or not, \ldots\ is an act of the understanding''. So conceived, the unity of the sensory manifold is actively provided by the understanding in intuition. Against this conception of synthesizing activity, \citet[226]{Prichard:1909yg} was right to claim that ``the act of combination cannot confer upon them or introduce into them a unity which they do not already possess''. In seeing the ripening tomato, the object of my sensory awareness, a particular material substance, already enjoys a substantial unity. This particular, with its substantial unity, is a constituent of a state of my consciousness. There is no need for synthesizing activity to provide for any unity in intuition. My sensory awareness already presents me with a substantial unity, the ripening tomato. If perception is a mode of taking in, the objects of sensory awareness are ``selectively made present, but not synthesized'' by our sensibility (in Johnston's \citeyear[285]{Johnston:2006uq} apt description). From this perspective, any felt need for synthesizing activity to confer unity upon sensory manifolds already represents a withdrawal from the world of sensible particulars. For if a particular were genuinely present, any needed unity would then be provided by the perceived particular itself.

McDowell avoids Prichard's objection by denying that understanding is active in intuition. Instead of unity being conferred in intuition by synthesizing activity, \citet[7]{McDowell:2008fk} claims that the unity is given in intuition. Moreover, as we have seen, he must maintain this, if his anticonjunctivism is to be sustained. According to McDowell, Kant's \citeyearpar[A79/B104--5]{Kant:1781fk} thesis does not require that understanding be active in intuition; rather, it requires only that the given be already in a form that could figure in the content of judgment:
\begin{quote}
	\ldots\ having an object present to one in an intuition is an actualization of capacities that are conceptual, in a sense that belongs with Kant's thesis that what accounts for the unity with which the associated content figures in intuition is the same function that provides for the unity of judgements. I have urged that even though the unity-providing function is a faculty for discursive activity, it is not in discursive activity that these capacities are operative in intuition. \ldots\ Nevertheless an intuition's content is all conceptual, in this sense: it is in the intuition in a form which one \emph{could} make it, that very content, figure in discursive activity. \citep[265]{McDowell:2008fk}
\end{quote}
Compare now McDowell's interpretation of the general framework of givenness:
\begin{quote}
	Givenness in the sense of the Myth would be an availability for cognition to subjects whose getting what is supposedly Given to them does not draw on capacities required for the sort of cognition in question. \citep[256]{McDowell:2008fk}
\end{quote}
It is only if the object is given in perception in a form that could figure in the content of discursive activity, paradigmatically, in judgment or assertion, that the Myth of the Given is avoided. For it is only if the object of perception is given in a form that could figure in discursive activity that perception can make available knowledge of that object. 

One cannot be given what one lacks the capacity to receive. On at least that much, we can all agree. For, as \citet{Travis:2008uq} emphasizes, this is a triviality. It is both substantive and controversial to claim that givenness, in the non-Mythical sense, \emph{requires} the unity-providing function of a faculty of discursive activity, even in the minimal sense of the given being already in a form that could figure in the content of discursive activity. After all, there is an alternative. Consider the conception of perception as a mode of taking in dogmatically sketched in section~\ref{sec:sensory_awareness}. Vision afford the perceiver with a sensory mode of awareness of particulars spatially distant from the perceiver's body. Not only is this sensory mode of awareness not propositional in the sense that it takes a particular as its object, neither is it in any way the actualization of the subject's conceptual capacities. Nevertheless, sensory awareness makes the subject knowledgeable of its object in the sense that it makes knowledge about its object available to the perceiving subject. It does so because of an alethic connection between the objects of perception and potentially known propositions. The yellowish red of the tomato that I see makes it true that the tomato is yellowish red. Awareness of the sensible truthmaker of a proposition affords the subject with a reason that is in this way akin to proof---it is logically impossible for the particular to exist and the proposition to be false. Since it is logically impossible for the yellowish red of the tomato to exist and the proposition that the tomato is yellowish red to be false, vision affords me a reason that warrants my coming to know that the tomato is yellowish red. The warrant is an epistemic entitlement, and a perceiver may possess this entitlement even if, in the circumstances of perception, they lack the conceptual capacities to know the relevant proposition. The particular present in sensory awareness is a reason that grounds the subject's epistemic entitlement, but not by being in a form that could figure in the content of judgment. % As \citet[44]{Prichard:1909yg} observed, having a form that could figure in the content of judgment is to have a kind of generality that precludes particulars. But awareness of particulars makes me knowledgeable of the world without the mind, nonetheless. 

That a coherent, natural alternative exists undermines the thought that givenness, in the non-Mythical sense, \emph{requires} being already in a form that could figure in the content of discursive activity. It is at least unobvious that it does. Moreover, a doubt about how, according to \citet{McDowell:2008fk}, perception could be both nondiscursive and conceptual motivates this natural alternative.

Intuitions are nondiscursive, in part, because they are not acts. The paradigm of discursive activity is assertion, an overt public performance. Judgment is discursive since it is the inner analogue of assertion. While not a public performance, like assertion, judgment is an act. Intuition differs from judgment and assertion in precisely this way. As \citet[chapter 9]{Prichard:1909yg} argued, the unified content is given in intuition and not actively synthesized by the discursive faculty of understanding. Intuitions, however, are nondiscursive in a further sense. Both judgment and assertion are ways of making something explicit (in Brandom's, \citeyear{Brandom:1994fk}, terminology). Since discursive acts are ways of making explicit, the contents of discursive acts are articulations. However, the unified content given in intuition is unarticulated, if articulable. Since the unified content of intuition is \emph{unarticulated}, it is not the content of a discursive act. Since the unified content of intuition is \emph{articulable}, it already has a form that could figure in the content of discursive acts and is, in that sense, conceptual:
\begin{quote}
	Visual intuitions typically present one with visible characteristics of objects that one is not equipped to attribute to the objects by making appropriate predications in claims or judgements. To make such an aspect of the content of an intuition into the content associated with a capacity that is discursive in the primary sense, one would need to carve it out, as it were, from the categorically unified but as yet unarticulated content of the intuition by determining it to be the meaning of a linguistic expression, which one thereby sets up as a means for making the content explicit.
\end{quote}
However, the sense in which the content of perception can reasonably be said to be unarticulated conflicts with its already having a form that could figure in the content of discursive activity. The conflation, in this passage, of exemplification and predication masks this conflict.

Consider how McDowell's conception of the unarticulated given converges on the conception C.I.\ \citet{Lewis:1929fk} develops in \emph{Mind and the World Order}. Just as McDowell aims to reconcile what is correct in Kant's idealist philosophy with an Aristotelian realism, Lewis aims to reconcile what is correct in Royce's idealist philosophy with the realism of his day. Whereas Royce held that experience always involves interpretation or conceptualization, realists, such as \citet{Russell:1912uq} and \citet{Moore:1903uo}, held that the objects of sensory awareness are independent of that awareness. The basis of Lewis' reconciliation is the distinction between what is given to the the mind, and the interpretation that the mind imposes on what is given. And just as McDowell thinks that vision presents us with visible characteristics that we are not equipped to predicate, the given, as \citet[52]{Lewis:1929fk} conceives of it, is incompletely describable since ``in describing it, in whatever fashion, we qualify it by bringing it under some category or other, select from it, emphasize aspects of it, and relate it in particular and avoidable ways.'' It is on these grounds that Lewis claims that the given is ineffable. But being ineffable is precisely to lack a form that could figure in the content of discursive activity.

McDowell can agree that in describing, in whatever fashion, what is given in perception, we qualify it by bringing it under some category or other---that is just the predicative component of perceptual judgment. He can also agree that we select from what is given in perception, at least in the sense of selecting an aspect of its discursive form to articulate. In articulating an aspect of the categorically unified if unarticulated content, we emphasize that aspect, at least over those other aspects that remain unarticulated. Moreover, it often happens that we  relate the object of perception in particular and avoidable ways. But McDowell would claim that Lewis goes too far in concluding, on this basis, that the given is ineffable. Every aspect of the unarticulated given is articulable, even if not every aspect is, or could be, articulated.

But the grounds that Lewis offers for the ineffability of the given can be understood in a way that is not so easily dismissed. Lewis can be read as echoing and elaborating Prichard's \citeyearpar[44]{Prichard:1909yg} distinction between thoughts and particulars. The first ground that Lewis offers is Prichard's---having a form that could figure in the content of discursive activity is to have a generality that precludes particulars. In describing, in whatever fashion, what is given in perception, we qualify it by bringing it under some category or other. In bringing a particular that we see under some category we relate it to a range of cases, those cases where the category correctly applies \citep[see][]{Travis:2005ys,Travis:2008uq}. Frege puts the point this way:
\begin{quote}
	A thought always contains something reaching out beyond the particular case so that this is presented to us as falling under something general. \citep[4]{Frege:1882uq}
\end{quote}
Lewis also emphasizes the way in which a particular can exceed what is represented in thought, just as what is represented in thought can exceed what is present in the particular. But it is the generality of thought that grounds the categorical distinction, and it is this which is not so easily dismissed. If thoughts are categorically distinct from particulars, and particulars are given in perception, then what is given in perception is not so much unarticulated as it is inarticulable. The yellowish red of the tomato may be the object of my visual awareness, but it is thoughts about the color of the tomato, and not the color of the tomato itself, that are articulable in judgment and assertion. Vision is, if not blind, then dumb \citep[see][]{Austin:1962lr,Travis:2004kx}.

% Not only do thoughts have a generality that precludes particulars, but the presented particular exceeds what is represented in thought, just as what is represented in thought can exceed the presented particular. The next two grounds involve properties of particulars not represented in thought. In perceptual judgment we select from what is given, in that the particular manifests, even to that partial perspective, indefinitely many objective regularities not represented in that judgement. Moreover in representing an aspect of the presented particular we inevitably emphasize that aspect over the other aspects that go unrepresented. In these ways, the particular exceeds what is represented in thought. The final ground that Lewis offers involves properties represented in thought that are extrinsic to the particular. It often happens that in judgement we relate to the object of perception in particular and avoidable ways. In relating to the object in particular and avoidable ways, thought represents properties extrinsic to the particular. In this way, what is represented in thought exceeds what is present in the particular. The grounds that Lewis offers for the ineffability of the given echo and elaborate Prichard's grounds for the distinction between thoughts and particulars.

% (Though perhaps this is not to understand them as Lewis understands them. According to Lewis, ordinary material particulars are not given in perception. Material substances persist through time, while the given exists only in the specious present. However, I precisely want to allow particular material substances to be present in visual awareness.) 

Consider the striking \emph{aporia} of McDowell's talk of carving out an aspect of the unarticulated if articulable given. Carving is most naturally read as imposing form, but the object of perception is meant already to have a form that could figure in discursive acts. An object with a form that could figure in discursive activity is meant to be selectively presented, not synthesized, by visual sensibility. Moreover, the metaphor of carving is best understood as analyzing a content of a possible judgment in something like Frege's \citeyearpar[§64]{Frege:1884fk} sense. So understood, to carve out an aspect of the unarticulated content is to determine the content of a predication under some appropriate analysis of the unarticulated content. But consider the way a visible characteristic of an object, the yellowish red of the tomato, say, is manifest in sensory consciousness. The yellowish red of the tomato is manifest in sensory consciousness by being present in that consciousness. The exemplification of color properties is among the aspects of the mind-independent environment that vision presents. The yellowish red of the tomato is distinct from the content of a possible predication. But according to McDowell, the visible characteristic is an aspect of the unarticulated content of intuition that is isolable and can be the meaning of a linguistic expression which would be the means for making that content explicit. McDowell misconceives sensory presentation as conceptual representation, in part, by conflating property exemplification with the content of a possible predication \citep[see][for a similar criticism of the Woodbridge Lectures]{Johnston:2006uq}. The former is a world-bound property instance, the latter is an intension spread across modal space. The latter may be a means, when combined with an appropriate demonstrative element, of representing the former, but only the former is present in sensory consciousness.

The \emph{aporia} arises because the only reasonable sense in which the given is unarticulated conflicts with its having a form that could figure in the content of discursive activity. The yellowish red of the tomato that I see is unarticulated only in the vacuous sense of being inarticulable. Seeing the yellowish red of the tomato may make thoughts about that color available to me. But it is thoughts about the color of the tomato, and not the color of the tomato itself, that are articulable in judgment and assertion. The objects of perception may be particulars in a way that precludes them from having a form that could figure in the content of discursive activity, but vision makes the subject knowledgeable of spatiotemporal particulars arrayed in a mind-independent environment. It does so because of the alethic connection between the particulars present in visual awareness and a range of potentially known propositions. Avoiding the Myth of the Given, if it is indeed a myth, does not require the unity-providing function of a faculty of discursive activity, not even in the minimal sense of the given being already in a form that could figure in the content of discursive activity. Conceptual capacities need not be actualized in perception for the subject in undergoing a perceptual experience to be knowledgeable of the world without the mind.


% section selective_presentation_and_synthesis (end)

\section{What Myth?} % (fold)
\label{sec:what_myth_}

Sellars and McDowell offer conceptions of perception tailor-made to avoid the Myth of the Given. McDowell was right in claiming that perceptual sensitivity is, or is constituted by, objects in the mind-independent environment being present in sensory awareness in a way that precludes perceptual sensitivity being a reductively identifiable independent factor in perception and, hence, guidance by manifolds of “sheer receptivity”. But McDowell was wrong in claiming that this requires conceptual capacities to be actualized in perceptual awareness. It is at least intelligible that a nonpropositional sensory mode of awareness could make us knowledgeable of particulars without the mind. Thus, criticism of conceptions of perception designed specifically to avoid the Myth of the Given naturally motivate a conception which is known, or at least reasonable judged, to be a form of the Myth. This is some reason, at least, to think that the Myth of the Given is no myth. 

% Perception, conceived as a mode of taking in, does not involve the actualization of the subject's conceptual capacities. Nevertheless, not only is that conception consistent with anticonjunctivism, but it requires anticonjunctivism as well. Perception, so conceived, is constitutively linked to the objects of sensory awareness. As such, the guidance is supplied by the objects being present in sensory awareness. That conception also provided a reasonable interpretation of the unity of mind and world that perception affords: Perception is a state of the conscious subject that has, as part of its nature, an external particular as a constituent. 

A large measure of overall agreement remains. Perception makes knowledge of the mind-inde\-pen\-dent environment available to the perceiving subject---it constitutes a change in the subject's knowledge potential whether or not such knowledge is activated. It does so by providing the subject with an epistemic warrant. This warrant is an entitlement to judge, where so judging is coming to know. The warrant is not a factor in terms of which knowledge could be analyzed or otherwise explained. One can possess this warrant without having the conceptual capacities to judge as is warranted. Moreover, perceptual sensitivity is, or is constituted by, perceptual awareness. Perceptual awareness may be a mode of sensitivity, but perceptual awareness is not analyzable or otherwise explained in terms of sensitivity reductively understood. Importantly, this is part of the explanation for why perception is a source of epistemic warrant. Perception is guided from without by particulars in the mind-independent environment being present in perceptual awareness. If perception is not merely causally or counterfactually but constitutively linked to particulars in the mind-independent environment, then the perceptual experience could not be the experience that it is without the existence of its object. That is why perceptual experience affords a subject with the appropriate recognitional capacities a reason that entitles them to know some range of propositions. It is the presentation of the particular in sensory awareness, a particular whose existence is incompatible with the falsity of a proposition, that makes the subject knowledgeable of a world without the mind.

% If a state of a conscious subject has, as part of its nature, an external particular as a constituent, then the subject could not be in that state if that particular did not exist. The reasons of which we are aware in perception may not be propositional the way the premises in a proof are, but they have the modal profile of proof. And since the particular is a constituent of the perceptual experience, it is impossible for the subject to undergo that experience and that range of propositions to be false. 

The potential extent of agreement should be unsurprising. Both the present conception and McDowell's share a common ancestry in twentieth century Oxford realism \citep[see][]{Kalderon:2010fk,Marion:2000ai,Marion:2000kl}. Both are attempts to work out, in different ways, what Putnam describes as natural realism:
\begin{quote}
	The natural realist, in James's sense, in contrast, holds that successful perception is just a seeing, or hearing, or feeling, etc., of things ``out there,'' and not a mere affectation of a person's subjectivity by those things. I agree with James, as well as with McDowell, that the false belief that perception must be so analyzed is at the root of all the problems with the view of perception that, in one form or another, has dominated Western philosophy since the seventeenth century. \citep[454]{Putnam:1994kx}
\end{quote}
What remains is a substantive disagreement that arises at a fine level of theoretical description. It would be disingenuous to claim, in advance of further inquiry, that either party to this dispute has fallen prey to some antecedently understood myth about which there is widespread and noncollusive agreement.

% section what_myth_ (end)

% Bibligography
\bibliographystyle{plainnat} 
\bibliography{Philosophy} 

\end{document}